---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
  [![R-CMD-check](https://github.com/SDCA-tool/sdca-package/workflows/R-CMD-check/badge.svg)](https://github.com/SDCA-tool/sdca-package/actions)
  <!-- badges: end -->


# SDCA

The R Package for the SDCA Project

## Installation

Ensure you have system dependencies:

```sudo apt-get install -y libssl-dev libcurl4-openssl-dev libxml2-dev libudunits2-dev libgdal-dev```

and R dependences:

```
R -e 'if (!require("units")) install.packages("units");'
R -e 'if (!require("sf")) install.packages("sf");'
```

Install the package with **remotes** as follows:

```{r install, eval=FALSE}
install.packages("remotes")
remotes::install_github("SDCA-tool/sdca-package")
```

## Use

The primary use case of the package is working within the SDCA website. However users can test the code locally by drawing an intervention on the [website](dev.carbon.place), downloading the GeoJSON then.


```{r use, eval=FALSE}
library(sdca)
download_rasters() #first time only

# Send a design to the API to get data
dat <- geojson_api(path = "carbon-calculator-scheme-intervention.geojson")

# Process the input data using local = TRUE
results <- process_results(dat, local = TRUE)

# Convert results into R format
results <- jsonlite::fromJSON(results)

```


